CODECHECK: An Open Science initiative for the independent execution of computations underlying research articles during peer review improves reproducibility

### 2021-02-08 codecheck-paper.tex
tools and resources

To run the system, we rely on freely available infrastructure, more 
specifically GitHub and Zenodo.
The \texttt{codecheckers} \textbf{GitHub} organisation\footnote{
\url{https://github.com/codecheckers}} contains projects for managing the
project website, the community of codecheckers, community discussions,
forks of checked code repositories, and the main register of 
CODECHECKs. Both the website\footnote{
\url{https://codecheck.org.uk/}} and the register\footnote{
\url{https://codecheck.org.uk/register}} are hosted as GitHub
pages. The register is a single table in CSV format that
connects the certificate identifier with the repository associated with
a specific conducted CODECHECK. Each of these repositories, which 
currently can be hosted on GitHub or Open Science Framework (OSF), 
contains the CODECHECK metadata file \texttt{codecheck.yml}. The register
further contains a column for the type of check, e.g.,~community, journal,
or conference, and the respective GitHub issue where communications and 
assignments around a specific check are organised. No information is 
duplicated between the register and the metadata files. When a new
certificate is entered into the register, an automated process using the
continuous integration infrastructure of GitHub, GitHub Actions, retrieves
all metadata files and builds different representations of the register
for viewing (HTML) and for integration with other services (CSV, JSON).
\textbf{Zenodo} is an open repository for scientific data and documents. It
mints DOIs for deposits and ensures long-term availability of all digital
artefacts related to the project. The CODECHECK community on Zenodo
\footnote{\url{https://zenodo.org/communities/codecheck/}} includes 
certificates as well as the regularly archived register
\cite{codecheck_register_jan2021}.

A \textbf{custom R package}, \texttt{codecheck}\footnote{
\url{https://github.com/codecheckers/codecheck}}, is used to automate repetitive
tasks around the authoring of certificates and the management of the register.
For example, it includes scripts for the deposition of certificates and related 
files to Zenodo using the R package \texttt{zen4R} \cite{zen4r} and for the
register update process outlined above.
Codecheckers may choose to not use the package and rely on their own tools
for creating the certificate, even a regular word processor.
This flexibility is deliberate to accomodate different skill sets and unforseen technical advances or challenges.

These tools and resources demonstrate that a CODECHECK process can be
managed without infrastructure costs on freely available platforms.
The automation should ensure that more checks can
be conducted in the future, though having the process be managed by a paid CODECHECK
editor or further automation, e.g.,~with a bot, could improve turnaround time.
The only costs are the project's domain, which is negligible.
This means that the initiative's main resource are the \textbf{humans} needed
for managing the project and processes and the codecheckers.
All contributions currently rely on (partly grant-based) public funding
and volunteering.
Naturally, similar set-ups are conceivable, such as using GitLab.com or
a hosted GitLab instance and the GitLab continuous integration.

>>>>

We use freely available infrastructure, GitHub and Zenodo, to run our
system.  The \texttt{codecheckers} \textbf{GitHub}
organisation\footnote{ \url{https://github.com/codecheckers}} contains
projects for managing the project website, the codecheckers community
and its discussions, code repositories, and the main register of
CODECHECKs. Both the website\footnote{
  \url{https://codecheck.org.uk/}} and the register\footnote{
  \url{https://codecheck.org.uk/register}} are hosted as GitHub
pages. The register is a single table in CSV format that connects the
certificate identifier with the repository associated with a specific
conducted CODECHECK. Each of these repositories, which currently can
be hosted on GitHub or Open Science Framework (OSF), contains the
CODECHECK metadata file \texttt{codecheck.yml}. The register further
contains a column for the type of check, e.g.,~community, journal, or
conference, and the respective GitHub issue where communications and
assignments around a specific check are organised. No information is
duplicated between the register and the metadata files. The continuous
integration infrastructure of GitHub, GitHub Actions, is used to
automate the register for viewing (HTML) and for integration with
other services (CSV, JSON).  \textbf{Zenodo} is our preferred open repository for
storing certificates. It mints DOIs for deposits and ensures
long-term availability of all digital artefacts related to the
project. The CODECHECK community on Zenodo
\footnote{\url{https://zenodo.org/communities/codecheck/}} includes
certificates as well as the regularly archived register
\cite{codecheck_register_jan2021}.

A \textbf{custom R package}, \texttt{codecheck}\footnote{
  \url{https://github.com/codecheckers/codecheck}}, automates
repetitive tasks around authoring certificates and managing the
register.  It includes scripts to deposit certificates and related
files to Zenodo using the R package \texttt{zen4R} \cite{zen4r} and
for the register update process outlined above.  Codecheckers can
ignore this package, and use their own tools for creating
and depositing the certificate.  This flexibility  accommodates
different skill sets and unforseen technical advances or challenges.

These tools and resources demonstrate that a CODECHECK process can be
managed without infrastructure costs on freely available platforms.
The automation should ensure that more checks can be conducted in the
future, though having the process be managed by a paid CODECHECK
editor or further automation, e.g.,~with a bot, to reduce turnaround
time. Our main resource requirements are the \textbf{humans} needed for managing
the project and processes and the codecheckers.  All contributions
currently rely on (partly grant-based) public funding and
volunteering.
